04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
so many lda plots

j <- plotfacetresults2(LDA.gon, levelstiming, "hypothalamus", 20) + labs(x = NULL) + theme(axis.text.x = element_blank()) +
  theme(legend.position = "bottom") + guides(fill = guide_legend(nrow  = 1)) 
k <- plotfacetresults2(LDA.pit, levelstiming, "pituitary", 17) + theme(strip.text = element_blank()) + labs(x = NULL) + theme(axis.text.x = element_blank())
l <- plotfacetresults2(LDA.gon, levelstiming, "gonads", 15) + theme(strip.text = element_blank()) + 
   labs(x = NULL)

>>>>

j <- plotfacetresults2(LDA.gon, levelstiming, "hypothalamus", 20) + labs(x = NULL) + 
  theme(axis.text.x = element_blank()) +
  theme(legend.position = "top") + guides(fill = guide_legend(nrow  = 1)) 
k <- plotfacetresults2(LDA.pit, levelstiming, "pituitary", 17) + 
  theme(strip.text = element_blank()) + labs(x = NULL) + theme(axis.text.x = element_blank())
l <- plotfacetresults2(LDA.gon, levelstiming, "gonads", 15) + theme(strip.text = element_blank()) + 
   labs(x = NULL)
